\normalfont{disCOVIDer19}

### 2020-04-03 Documentation/article_4.tex
pub

The percentage indicator is calculated dividing the total number of COVID19 cases by the population of the respective region/province (the latter retrieved from Istat \cite{Istat+res0,Istat+res1}).
\begin{equation}
percentage~cases = \frac{total~cases}{local~population} \times 100
\end{equation}
This indicator ensures that the number of cases in more populated areas are not over-indexed compared to less populated ones. Similarly, it ensures less populated areas are not under-indexed. 
The density indicator accounts for the territorial extension (in $km^2$) of regions/provinces expressed in parts per thousand (\textperthousand ) and is calculated as follows:
\begin{equation}
density~cases =  \dfrac{total~cases}{territorial~extension}\times 1000
\end{equation}
This indicator combines the population density with infection spread, offering a control over space. Indeed, it is directly proportional to population density and to percentage cases:
\begin{equation}
density~cases =  \dfrac{total~cases}{local~population} \cdot \dfrac{local~population}{territorial~extension} \times 1000 = percentage~cases \cdot density~population \times 1000
\end{equation}
It is enhanced by densely populated territories, which, by the way, may in turn enhance spread infection too.
Finally, the summary statistics section (Fig. \ref{Home_fig3}) provides some barometer level statistics regarding the current total number of COVID19 cases in Italy with three further breakouts: intensive care, hospitalised, and home isolation.

>>>>

The percentage indicator is calculated dividing the total number of COVID19 cases by the population of the respective region/province (the latter retrieved from Istat \cite{Istat+res0,Istat+res1}).
\begin{equation}
percentage~cases = \frac{total~cases}{local~population} \times 100
\end{equation}
This indicator ensures that the number of cases in more populated areas are not over-indexed compared to less populated ones. Similarly, it ensures less populated areas are not under-indexed. 
The density indicator accounts for the territorial extension (in $km^2$) of regions/provinces expressed in parts per thousand (\textperthousand ) and is calculated as follows:
\begin{equation}
density~cases =  \dfrac{total~cases}{territorial~extension}\times 1000
\end{equation}
This indicator combines the population density with infection spread, offering a control over space. Indeed, it is directly proportional to population density and to percentage cases:
\begin{equation}
\begin{split}
density~cases & =   \dfrac{total~cases}{local~population} \cdot \dfrac{local~population}{territorial~extension} \times 1000 \\  & = percentage~cases \cdot density~population \times 1000
\end{split}
\end{equation}
It is enhanced by densely populated territories, which, by the way, may in turn enhance spread infection too.
Finally, the summary statistics section (Fig. \ref{Home_fig3}) provides some barometer level statistics regarding the current total number of COVID19 cases in Italy with three further breakouts: intensive care, hospitalised, and home isolation.
